Legacy Data Confounds Genomics Studies

### 2019-06-14 LatexManuscript/legacy.tex
edit

\begin{table}[h!]
\centering
\begin{tabular}{l  r r r}
                      & {Repeat}  & {Non-Repeat}   & {Total}    \\ \hline
{SNP}  & 3,369 \luke{(0.53\textperthousand)} & 11,059 (0.56\textperthousand) & 14,428\\  
{INDEL} & 181 (0.3\textperthousand) & 657 (0.66\textperthousand) & 838\\ \hline
{Total} & 3,550 & 11,716 & 15,270\\
\end{tabular}
\caption{Number of statistically significant variants  passing the 1000 Genomes Project strict mask per category. 
Variants that are flagged by the 1000 Genomes Project nested repeat mask file were analyzed separately for FDR calculation. SNPs and INDELs were also analyzed separately.
A total of 15,270 are statistically significantly associated to $Q$. 
The number of variants included in the analysis for SNPs, SNPs in repeat regions, INDELs and INDELs in repeat regions are  19,846,786, 6,312,620, 1,770,315 and 586,342 respectively.}
\label{sigTable}
\end{table}

>>>>

\begin{table}[h!]
\centering
\begin{tabular}{l  r r r}
                      & {Repeat}  & {Non-Repeat}   & {Total}    \\ \hline
{SNP}  & 3,369 \textcolor{gray}{0.53\textperthousand} & 11,059 \textcolor{gray}{0.56\textperthousand} & 14,428\\  
{INDEL} & 181 \textcolor{gray}{0.3\textperthousand} & 657 \textcolor{gray}{0.66\textperthousand} & 838\\ \hline
{Total} & 3,550 & 11,716 & 15,270\\
\end{tabular}
\caption{Number of statistically significant variants  passing the 1000 Genomes Project strict mask per category. 
Variants that are flagged by the 1000 Genomes Project nested repeat mask file were analyzed separately for FDR calculation. SNPs and INDELs were also analyzed separately.
A total of 15,270 are statistically significantly associated to $Q$. 
The number of variants included in the analysis for SNPs, SNPs in repeat regions, INDELs and INDELs in repeat regions are  19,846,786, 6,312,620, 1,770,315 and 586,342 respectively.}
\label{sigTable}
\end{table}
